---
title: "RMarkdown Outline"
author: "Connor Guest"
subtitle: "Use this to structure your reports"
date: "6/5/2019"
output: 
  html_document:
    theme: cosmo
    highlight: monochrome
    toc: true
    toc_float: true
    toc_depth: 4
    code_folding: hide
    number_sections: true
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[RMarkdown Specifics](https://bookdown.org/yihui/rmarkdown/html-document.html#appearance-and-style)

 [Find many more selectors and a full CSS reference on the Mozilla Developer Network.](https://developer.mozilla.org/en-US/docs/Web/CSS/CSS_Selectors)

## Set Up

#### **Option	Effect**
**include**	(Whether to show the R code chunk and its output.)   
**echo**	(Whether to show the R code chunk.)  
**message**	(Whether to show output messages.)  
**warning**	(Whether to show output warnings.)  
**eval**	(Whether to actually evaluate the R code chunk.)  
*Structured like this: echo=FALSE*  
[More options here](https://yihui.name/knitr/options/)

#### **Figure Options**
Option	- Possible Values	- Effect  
fig.height	- Numeric, inches	- The height of the image in inches.  
fig.width	- Numeric, inches	- The width of the image in inche.  
fig.align	- One of "left", "right" or "center"	- The alignment of the image in the report.  
[More options here](https://yihui.name/knitr/options/#plots)  
*{r, fig.height = 8, fig.width = 4.5, fig.align = "center"}*

#### Include a picture
![An impressive mountain](https://upload.wikimedia.org/wikipedia/commons/thumb/6/60/
Matterhorn_from_Domh%C3%BCtte_-_2.jpg/1200px-Matterhorn_from_Domh%C3%BCtte_-_2.jpg)

## Summary

This is where you are going to quickly summarize what you did.

The **Core Payments** team has many [data sets](https://www.notion.so/paystack/Transaction-Analysis-Guide-9f93edf05d7b4fadaf14642aa888853a) to create their monthly report.  
  
In this report, *we make a reproducible monthly report* that will be recreated with only a few monior adjustments each month.  


## Preparations
```{r message=FALSE}
library(tidyverse)
library()
```

This is where you will load the necessary R packages.

## Analysis

### Data

*This is where you will load the data.*

```{r loading_data}
load(url("http://s3.amazonaws.com/assets.datacamp.com/production/course_5807/datasets/ilo_data.RData"))
```

The loaded data contains `r count(ilo_data)` rows.  
Number of rows was calculated using in-line r code! Using *r count(ilo_data)*


### Preprocessing

This is where you will preprocess the data.

### Results

This is where you will plot the data.
